A 3D curvilinear skeletonization algorithm with application to path tracing

### 2012-12-05 skeleton_and_pathtracing.tex
Ajout de l'institut pour vence et laurent

\title{A 3D curvilinear skeletonization algorithm with application to path tracing}
\author{John Chaussard\inst{1} \and Laurent No\"{e}l\inst{2} \and Venceslas Biri\inst{2} \and Michel Couprie\inst{2}\thanks{This work has been partially supported by the \quotes{ANR-2010-BLAN-0205 KIDICO} project}}
\institute{Universit\'{e} Paris 13, Sorbonne Paris Cit\'{e}, LAGA, CNRS(UMR 7539), \\ F-93430, Villetaneuse, France \\ \email{chaussard@math.univ-paris13.fr}
\and
Universit\'{e} Paris Est, LIGM, A3SI-ESIEE \\ 2, boulevard Blaise Pascal, 93162 Noisy le Grand CEDEX, France \\ \email{laurent.noel@esiee.fr, v.biri@esiee.fr, michel.couprie@esiee.fr}}

@@

The collapse operation is the basic operation for performing homotopic thinning of a complex, and consists of removing two distinct faces $(f,g)$ from a complex $X$ under the condition that they form a free pair:

@@

\begin{figure}[tb]
\begin{center}
\begin{tabular}{cc|cc}
	\myincludegraphics{0.16\textwidth}{hand2.jpg} &
	\myincludegraphics{0.16\textwidth}{hand_curvskel.jpg} &
	\myincludegraphics{0.21\textwidth}{neptune.jpg} &
	\myincludegraphics{0.21\textwidth}{neptune_curvskel.jpg} \\
\end{tabular}
\caption[Results of algorithm \ref{algo::3d_curvskel}]{\label{fig::result_skel} \textbf{Results of algorithm \ref{algo::3d_curvskel}} for two shapes: a hand (left) and a statue (right). In each pair, the rightmost image represents the skeleton.}
\end{center}
\end{figure}

>>>>

\title{A 3D curvilinear skeletonization algorithm with application to path tracing}
\author{John Chaussard\inst{1} \and Laurent No\"{e}l\inst{2} \and Venceslas Biri\inst{2} \and Michel Couprie\inst{3}\thanks{This work has been partially supported by the \quotes{ANR-2010-BLAN-0205 KIDICO} project}}
\institute{Universit\'{e} Paris 13, Sorbonne Paris Cit\'{e}, LAGA, CNRS(UMR 7539), \\ F-93430, Villetaneuse, France \\ \email{chaussard@math.univ-paris13.fr}
\and
Universit\'{e} Paris Est, LIGM, CNRS(UMR 8049) \\ Cit\'{e} Descartes, 5 boulevard Descartes, 77454 Marne-la-Vallée CEDEX 22, France \\ \email{laurent.noel@esiee.fr, v.biri@esiee.fr}
\and
Universit\'{e} Paris Est, LIGM, A3SI-ESIEE, CNRS(UMR 8049) \\ 2, boulevard Blaise Pascal, 93162 Noisy le Grand CEDEX, France \\ \email{michel.couprie@esiee.fr}
}

@@

The collapse operation is the basic operation for performing homotopic thinning of a complex, and consists of removing free pairs of faces:

@@

\begin{figure}[tb]
\begin{center}
\begin{tabular}{cc|cc}
	\myincludegraphics{0.20\textwidth}{hand2.jpg} &
	\myincludegraphics{0.20\textwidth}{hand_curvskel.jpg} &
	\myincludegraphics{0.21\textwidth}{neptune.jpg} &
	\myincludegraphics{0.21\textwidth}{neptune_curvskel.jpg} \\
\end{tabular}
\caption[Results of algorithm \ref{algo::3d_curvskel}]{\label{fig::result_skel} \textbf{Results of algorithm \ref{algo::3d_curvskel}} for two shapes: a hand (left) and a statue (right). In each pair, the rightmost image represents the skeleton.}
\end{center}
\end{figure}
